Out-of-Sample Comparisons of Overfit Models

### 2014-02-26 paper.tex
Change fonts to charter and source code pro
This commit changes the main font in the paper to Bitstream Charter
and changes the monospaced font (where it's used) to Adobe's Source
Code Pro.

\documentclass[11pt]{article}
\usepackage{tikz,setspace}
\usetikzlibrary{calc}
\usetikzlibrary{fit}
\usepackage[round]{natbib}
\usepackage[margin=1in]{geometry}
\onehalfspacing
\input{macros}
\usepackage[charter]{mathdesign}

@@

@@

\clearpage
\begin{figure}
  \centering {\large Simulated Coverage of One-Sided DMW Interval for
    $\E_R\oosA$} \input{mc/plots/interval-testerror1.tikz}
\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
  one-sided interval based on the DMW
  OOS test, plotted as a function of the fraction of
  observations used in the test sample, $P/T$.  The solid horizontal
  line denotes the intervals' nominal coverage.}
 \label{fig:interval-R}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Coverage of One-Sided DMW Interval for
    $\E_T\oosB$} \input{mc/plots/interval-generror1.tikz}
\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
  one-sided interval based on the DMW
  OOS, plotted as a function of the fraction of
  observations used in the test sample, $P/T$.  The solid horizontal
  line denotes the intervals' nominal coverage.}
\label{fig:interval-T}
\end{figure}
\clearpage

\begin{figure}
  \centering {\large Simulated Rejection Probability of $F$-test Under
    $\E_T \oosB \leq 0$}
  \input{mc/plots/ftest-001.tikz}
  \caption{Simulated rejection probabilities for the $F$-test given
    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
    10\% indicate that the test rejects the benchmark model too often.
    See Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ftest}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of Clark and West
    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
  \input{mc/plots/size-clarkwest.tikz}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) OOS test statistic given $\E_T \oosB
    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
    that the test rejects the benchmark model too often.  The solid
    horizontal line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
   \label{fig:clarkwest}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of McCracken
    (2007) Test \\ Under $\E_T \oosB \leq 0$}
  \input{mc/plots/size-mccracken.tikz}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    OOS test statistic given $\E_T \oosB \leq 0$ with
    nominal size 10\%.  Values greater than 10\% indicate that the
    test rejects the benchmark model too often.  The solid horizontal
    line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB > 0$} \input{mc/plots/size-dmwpower.tikz}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB > 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-power}
\end{figure}

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (OLS)}
\input{empirics/plots/oos-mse-1.tikz}
\input{empirics/plots/oos-mse-1b.tikz}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics1}
\end{figure}

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (CT)}
\input{empirics/plots/oos-mse-2.tikz}
\input{empirics/plots/oos-mse-2b.tikz}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the 
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics2}
\end{figure}

\begin{figure}
\centering
\large{OOS MSE of Individual Forecasts of Equity Premium}
\input{empirics/plots/oos-ind-ks.tikz}
\input{empirics/plots/oos-ind-pm.tikz}
\caption{OOS MSE of the Prevailing Mean (PM) and
    Kitchen Sink (KS) models for equity premium prediction as
    a function of the size of the training sample, $R$.  Please note
    that the vertical scales are different in the two plots.}
\label{fig:empirics3}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage{tikz,setspace}
\usetikzlibrary{calc}
\usetikzlibrary{fit}
\usepackage[round]{natbib}
\usepackage[margin=1in]{geometry}
\onehalfspacing
\input{macros}
\usepackage[charter]{mathdesign}
\usepackage[osf]{sourcecodepro}
% This will make copy and pasting easier, and will prevent the
% abomination that is monospace font ligatures.  Sorry, everyone who
% really likes ligatures.  Don't worry, the Bitstream Charter font
% has very, very few ligatures anyway.
\DisableLigatures{family = tt*}
\urlstyle{same}

@@

\usepackage[bitstream]{mathdesign}

@@

\clearpage
\begin{figure}
  \centering {\large Simulated Coverage of One-Sided DMW Interval for
    $\E_R\oosA$} \input{floats/mc-interval-testerror1.tex}
\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
  one-sided interval based on the DMW
  OOS test, plotted as a function of the fraction of
  observations used in the test sample, $P/T$.  The solid horizontal
  line denotes the intervals' nominal coverage.}
 \label{fig:interval-R}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Coverage of One-Sided DMW Interval for
    $\E_T\oosB$} \input{floats/mc-interval-generror1.tex}
\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
  one-sided interval based on the DMW
  OOS, plotted as a function of the fraction of
  observations used in the test sample, $P/T$.  The solid horizontal
  line denotes the intervals' nominal coverage.}
\label{fig:interval-T}
\end{figure}
\clearpage

\begin{figure}
  \centering {\large Simulated Rejection Probability of $F$-test Under
    $\E_T \oosB \leq 0$}
  \input{floats/mc-ftest.tex}
  \caption{Simulated rejection probabilities for the $F$-test given
    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
    10\% indicate that the test rejects the benchmark model too often.
    See Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ftest}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize.tex}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of Clark and West
    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
  \input{floats/mc-clarkwestsize.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) OOS test statistic given $\E_T \oosB
    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
    that the test rejects the benchmark model too often.  The solid
    horizontal line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
   \label{fig:clarkwest}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of McCracken
    (2007) Test \\ Under $\E_T \oosB \leq 0$}
  \input{floats/mc-mccrackensize.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    OOS test statistic given $\E_T \oosB \leq 0$ with
    nominal size 10\%.  Values greater than 10\% indicate that the
    test rejects the benchmark model too often.  The solid horizontal
    line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB > 0$} \input{floats/mc-dmwpower.tex}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB > 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-power}
\end{figure}

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (OLS)}
\input{floats/empirics-oos-mse-1.tex}
\input{floats/empirics-oos-mse-1b.tex}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics1}
\end{figure}

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (CT)}
\input{floats/empirics-oos-mse-2.tex}
\input{floats/empirics-oos-mse-2b.tex}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the 
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics2}
\end{figure}

\begin{figure}
\centering
\large{OOS MSE of Individual Forecasts of Equity Premium}
\input{floats/empirics-oos-ind-ks.tex}
\input{floats/empirics-oos-ind-pm.tex}
\caption{OOS MSE of the Prevailing Mean (PM) and
    Kitchen Sink (KS) models for equity premium prediction as
    a function of the size of the training sample, $R$.  Please note
    that the vertical scales are different in the two plots.}
\label{fig:empirics3}
\end{figure}
